quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-07 paper-quollr.Rmd
Added scratch to find defaults

```{r, echo=TRUE}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 15, r2 = r2, 
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x")
```

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r, echo=TRUE}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 15, r2 = r2, 
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x"
  )
```

@@

```{r, echo=TRUE}
calc_bins_y(
  bin1 = 10, 
  r2 = r2
  )
```

@@

```{r, echo=TRUE}
hex_binning(
  data = s_curve_noise_umap_scaled, 
  bin1 = 10, 
  r2 = r2
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
tr1_object <- tri_bin_centroids(
  hex_df = df_bin_centroids, 
  x = "c_x", 
  y = "c_y"
  )

tr_from_to_df <- gen_edges(
  tri_object = tr1_object
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
umap_data_with_hb_id <- hb_obj$data_hb_id

df_all <- bind_cols(
  s_curve_noise_training |> dplyr::select(-ID), 
  umap_data_with_hb_id
  )

df_bin <- avg_highd_data(
  data = df_all, 
  col_start = "x"
  )
```

@@

### Choice of bins

### Removal of low-density bins

```{r, echo=TRUE, eval=FALSE}

find_low_dens_hex(
  df_bin_centroids_all = df_bin_centroids, 
  bin1 = num_bins_x, 
  df_bin_centroids_low = df_bin_centroids_low
  )

### Removing long edges

```{r, echo=TRUE, eval=FALSE}
find_lg_benchmark(
  distance_edges = distance_df, 
  distance_col = "distance"
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
vis_lg_mesh(
  distance_edges = distance_df, 
  benchmark_value = 0.75, 
  tr_coord_df = tr_from_to_df, 
  distance_col = "distance"
  )
```

```{r, echo=TRUE, eval=FALSE}
vis_rmlg_mesh(
  distance_edges = distance_df, 
  benchmark_value = 0.75, 
  tr_coord_df = tr_from_to_df, 
  distance_col = "distance"
  )
```

@@

```{r, echo=TRUE, eval=FALSE}
show_langevitour(
  df = df_all, 
  df_b = df_bin, 
  df_b_with_center_data = df_bin_centroids, 
  benchmark_value = 0.75, 
  distance = distance_df, 
  distance_col = "distance", 
  use_default_benchmark_val = FALSE, 
  col_start = "x"
  )
```
